TBD

### 2021-03-12 outputs/paper/paper.Rmd
prelim code for first model
S8 within supplementary materials for the paper.

library(tidyverse)
library(ggplot2)
library(ggalt)
library(ggthemes)
library(kableExtra)
library(janitor)
library(dplyr)
```

@@

```{r, echo = FALSE, message = FALSE}
### Import the cleaned data
dfCleanBehav <- readr::read_csv("../../inputs/data/clean_behavioral-data.csv")

### All wallets with no money
dfNoMoney <- 
  dfCleanBehav %>%
  filter(cond == 0) %>%
  group_by(country_2) %>%
  tally()

@@

>>>>

library(tidyverse)
library(ggplot2)
library(ggalt)
library(ggthemes)
library(kableExtra)
library(janitor)
library(dplyr)
library(olsrr)

### Import the cleaned data
dfCleanBehav <- readr::read_csv("../../inputs/data/clean_behavioral-data.csv")
dfBehavModel <- readr::read_csv("../../inputs/data/clean_behavioral-data_model.csv")
```

@@

```{r, echo = FALSE, message = FALSE}
### All wallets with no money
dfNoMoney <- 
  dfCleanBehav %>%
  filter(cond == 0) %>%
  group_by(country_2) %>%
  tally()

@@

```{r S8, echo = FALSE, message = FALSE}

### OLS formula : y = mx + c, where 
### y = response (dependent variable) - so report/no report,
### m = slope
### x = independent variable, predictor - condition (no money, money, big money)
### c = the intercept
s8_money <-
  dfBehavModel %>%
  filter(cond == 1 | cond == 2 | cond == 3)
ols_regress(response ~ cond + male + age + computer + coworkers + other_bystanders, data = s8_money)

s8_no_money <-
  dfBehavModel %>%
  filter(cond == 0)
ols_regress(response ~ cond + male + age + computer + coworkers + other_bystanders, data = s8_no_money)

# need to control for treatment + institution + city 
```

```{r S9, echo = FALSE, message = FALSE}
